---
title: "Preliminary Conjoint Analysis"
author: "Nora Kirkizh and Sebastian Stier"
date: "01/04/2020"
output:
  pdf_document: default
  html_document: default
---

```{r, include=FALSE}

rm(list=ls())

library(tidyverse)
library(jtools)
library(rio)
library(cregg)
library(ggplot2)
library(gridExtra)
library(expss)
library(tidyr)
library(data.table)
library(plyr)

requireNamespace("xtable", quietly = TRUE)
# load data
conjoint <- cj_df(rio::import("../Output/conjoint_plotting_data.RData"))
conjoint[, 2:16] <- NULL

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width=13, fig.height=5, message=FALSE, warning=FALSE)
```

## Introduction

This is an R Markdown report on preliminary analysis of conjoint survey experiment output. The conjoint survey experiment aimed to test hypotheses on populist radical right voters policy preferences. Voters were asked to evaluate eight pairs of profiles of candidates for a parliament seat in a corresponding country. Voters from France, italy, Spain, and Germany took part in the survey experiment or 1951 voters in total, whcih resulted in 31216 evaluated candidate rofiles. We are adopting the code from <https://github.com/leeper/conjoint-subgroups>. Plots by party identification, country of residence, and other political attitudes and sociodemographic background features can be found here.

## AMCE vs. Marginal Means

AMCE against marginal means based on pooled data meaning for all countries and voters combined.

```{r AMCE vs MM pooled data plots, echo=FALSE}

# AMCE plot with pooled data
p1 <- plot(
  cregg::cj(
    conjoint, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "amce"
  ), vline = 0
) + 
  ggplot2::scale_x_continuous(
    limits = c(-0.4, 0.4), 
    breaks = c(-0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4)
  ) + 
  ggplot2::geom_text(
    aes(label = ifelse(is.na(std.error), "", sprintf("%0.2f (%0.2f)", estimate, std.error))),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none") + ggtitle("All voters")


# MM plot with pooled data
p2 <- plot(
  cregg::cj(
    conjoint, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.2, 0.3, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none") + ggtitle("All voters")

# place plots next to each other for comparison
gridExtra::grid.arrange(p1, p2, ncol=2)
```

## Plots by group: all countries

```{r Plots by group, echo=FALSE}

# MM plot with PRRV
PRRV <- conjoint[conjoint$group == "PRRV",]

p_prrv <- plot(
  cregg::cj(
    PRRV, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.2, 0.3, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none") + ggtitle("Populist radical right")


# MM plot with nonPRRV
nonPRRV <- conjoint[conjoint$group == "nonPRVV",]

p_nonprrv <- plot(
  cregg::cj(
    nonPRRV, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.2, 0.3, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none") + ggtitle("non-Populist radical right")


gridExtra::grid.arrange(p_prrv, p_nonprrv, ncol=2)

```

## Plots by Country

The plots illustrate marginal means for PRVV and nonPRRV voters by country.

```{r MM by country on a single plot, fig.width=15, fig.height=6}

allprrv <- conjoint %>% filter(group == "PRRV")
allnonprrv <- conjoint %>% filter(group == "nonPRVV")

p_allprrv <- plot(cj(allprrv, selected ~ imm + soc + climate + eu + run, id = ~ panelist_id, by = ~ country, estimate = "mm"), group = "BY", vline = 0.5) + ggtitle("Populist radical right")

p_allnonprrv <- plot(cj(allnonprrv, selected ~ imm + soc + climate + eu + run, id = ~ panelist_id, by = ~ country, estimate = "mm"), group = "BY", vline = 0.5) + ggtitle("non-Populist radical right")

gridExtra::grid.arrange(p_allprrv, p_allnonprrv, ncol=2)

```

#### Germany

```{r plots with germany, echo=FALSE, error=FALSE}

# MM plot with German PRRV 
ger_prrv <- conjoint %>% filter(group == "PRRV" & country == "Germany")

p_ger_prrv <- plot(
  cregg::cj(
    ger_prrv, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.2, 0.3, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none") + ggtitle("AfD")

# MM plot with German nonPRRV
ger_nonprrv <- conjoint %>% filter(group == "nonPRVV" & country == "Germany")

p_ger_nonprrv <- plot(
  cregg::cj(
    ger_nonprrv, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.2, 0.3, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none") + ggtitle("All other voters")

gridExtra::grid.arrange(p_ger_prrv, p_ger_nonprrv, ncol=2)

```

#### France

```{r France, }

# subset PRRV and nonPRRV
fr_prrv <- conjoint %>% filter(group == "PRRV" & country == "France")
fr_nonprrv <- conjoint %>% filter(group == "nonPRVV" & country == "France")

# MM with French PRRV
p_fr_prrv <- plot(
  cregg::cj(
    fr_prrv, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.2, 0.3, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none") + ggtitle("RN, Marine Le Pen")

# MM plot with France nonPRRV
p_fr_nonprrv <- plot(
  cregg::cj(
    fr_nonprrv, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.2, 0.3, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none") + ggtitle("All other voters")

gridExtra::grid.arrange(p_fr_prrv, p_fr_nonprrv, ncol=2)

```

#### Italy

```{r Italy, }

# subset PRRV and nonPRRV
it_prrv <- conjoint %>% filter(group == "PRRV" & country == "Italy")
it_nonprrv <- conjoint %>% filter(group == "nonPRVV" & country == "Italy")

# MM with Italian PRRV
p_it_prrv <- plot(
  cregg::cj(
    it_prrv, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.2, 0.3, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none") + ggtitle("Lega Nord, FdI")

# MM plot with Italian nonPRRV
p_it_nonprrv <- plot(
  cregg::cj(
    it_nonprrv, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.2, 0.3, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none") + ggtitle("All other voters")

gridExtra::grid.arrange(p_it_prrv, p_it_nonprrv, ncol=2)

```


#### Spain

```{r Spain, }

# subset PRRV and nonPRRV
es_prrv <- conjoint %>% filter(group == "PRRV" & country == "Spain")
es_nonprrv <- conjoint %>% filter(group == "nonPRVV" & country == "Spain")

# MM with Spain PRRV
p_es_prrv <- plot(
  cregg::cj(
    es_prrv, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.2, 0.3, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none") + ggtitle("Vox")

# MM plot with Spain nonPRRV
p_es_nonprrv <- plot(
  cregg::cj(
    es_nonprrv, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm"
  ), vline = 0.5
) + 
  ggplot2::scale_x_continuous(
    limits = c(0.1, 0.9), 
    breaks = c(0.1, 0.2, 0.2, 0.3, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
  ) + 
  ggplot2::geom_text(
    aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)),
    colour = "black", 
    size = 2,
    position = position_nudge(y = .5)
  ) + 
  theme(legend.position="none") + ggtitle("All other voters")

gridExtra::grid.arrange(p_es_prrv, p_es_nonprrv, ncol=2)

```

```{r list of parties in the sample, }

df_parties <- conjoint %>% select(partyidcloseW1.x, country.x) %>% 
  group_by(country.x, partyidcloseW1.x) %>% 
  summarise(count=n())

print(xtable::xtable(df_parties))

# library(kableExtra)
# library(magrittr)
# kable(df_parties, "html") %>%
  # kable_styling(bootstrap_options = c("striped", "hover")) %>%
  # cat(., file = "parties.html")



```

```{r recoding parties according to PopuList, }

conjoint$partyID_type <- revalue(conjoint$partyidcloseW1, c(
  # mainstream
  "Génération.s, le mouvement" = "mainstream",
  "SPD" = "mainstream",
  "FDP" = "mainstream",
  "Partito Democratico (PD)" = "mainstream",
  "PSOE" = "mainstream",
  # mainstream right
  "La République En Marche!" = "mainstream right",
  "Les Républicains" = "mainstream right",
  "CDU/CSU" = "mainstream right",
  "+Europa / Radicali" = "mainstream right",
  "PP" = "mainstream right",
  # right-wing populist parties (or far-right?)
  "AfD" = "right-wing populist", 
  "Rassemblement national" = "right-wing populist",
  "Lega" = "right-wing populist",
  "Fratelli d'Italia" = "right-wing populist", 
  "VOX" = "right-wing populist",
  "Debout la France" = "right-wing populist",
  # left-wing populist
  "La France Insoumise" = "left-wing populist",
  "Compromís" = "left-wing populist",
  "En Comú Podem" = "left-wing populist",
  "Linke" = "left-wing populist",
  "Podemos" = "left-wing populist",
  # populist
  "Forza Italia" = "populist",
  "Gilets Jaunes" = "populist",
  "Movimento 5 Stelle" = "populist",
  "Potere al Popolo (PaP)" = "populist",
  # left-wing
  "EH Bildu" = "left-wing",
  "En Marea" = "left-wing",
  "ERC" = "left-wing",
  "Foro Asturias" = "left-wing",
  "IU" = "left-wing",
  "Liberi e Uguali (LEU)" = "left-wing",
  # centre-left
  "Europe Écologie Les Verts" = "centre-left",
  "Grüne" = "centre-left",
  "Mouvement radical" = "centre-left",
  "Parti socialiste" = "centre-left",
  # centre-right
  "EAJ-PNV" = "centre-right",
  "Ciudadanos" = "centre-right",
  "Agir, la droite constructive" = "centre-right",
  # right
  "La Destra" = "right",
  # centre
  "Mouvement démocrate" = "centre",
  "PDeCAT" = "centre",
  "Union des démocrates et indépendants" = "centre"))


conjoint$partyvoteW2_type <- revalue(conjoint$partyvoteW2_chr, c(
  # mainstream
  "Benoit Hamon" = "mainstream",
  "SPD" = "mainstream",
  "FDP" = "mainstream",
  "Partito Democratico (PD)" = "mainstream",
  "PSOE" = "mainstream",
  # mainstream right
  "Emmanuel Macron" = "mainstream right",
  "Francois Fillon" = "mainstream right",
  "CDU/CSU" = "mainstream right",
  "+Europa / Radicali" = "mainstream right",
  "PP" = "mainstream right",
  "Unione di Centro / Noi con l'Italia" = "mainstream right",
  # right-wing populist parties (or far-right?)
  "AfD" = "right-wing populist", 
  "Marine Le Pen" = "right-wing populist",
  "Lega" = "right-wing populist",
  "Fratelli d'Italia" ="right-wing populist", 
  "VOX" = "right-wing populist",
  "Nicolas Dupont-Aignan" = "right-wing populist",
  # left-wing populist
  "Jean-Luc Melenchon" = "left-wing populist",
  "Compromis" = "left-wing populist",
  "En Comu Podem" = "left-wing populist",
  "Linke" = "left-wing populist",
  "Podemos" = "left-wing populist",
  # populist
  "Forza Italia" = "populist",
  "Movimento 5 Stelle" = "populist",
  "Potere al Popolo" = "populist",
  # left-wing
  "EH Bildu" = "left-wing",
  "ERC" = "left-wing",
  "Liberi e Uguali" = "left-wing",
  # centre-left
  "Grüne" = "centre-left",
  "PACMA" = "centre-left",
  # centre-right
  "EAJ-PNV" = "centre-right",
  "Ciudadanos" = "centre-right",
  # right
  "La Destra" = "right",
  # centre
  "PDeCAT" = "centre"))


conjoint$eupartyIDw1_type <- revalue(conjoint$eucomingvotepartyW1, c(
  # mainstream
  "Génération.s, le mouvement" = "mainstream",
  "SPD" = "mainstream",
  "FDP" = "mainstream",
  "Partito Democratico (PD)" = "mainstream",
  "PSOE" = "mainstream",
  # mainstream right
  "La République En Marche!" = "mainstream right",
  "Les Républicains" = "mainstream right",
  "CDU/CSU" = "mainstream right",
  "+Europa / Radicali" = "mainstream right",
  "PP" = "mainstream right",
  # "Unione di Centro / Noi con l'Italia" = "mainstream right",
  # right-wing populist parties (or far-right?)
  "AfD" = "right-wing populist", 
  "Rassemblement national" = "right-wing populist",
  "Lega" = "right-wing populist",
  "Fratelli d'Italia" ="right-wing populist", 
  "VOX" = "right-wing populist",
  "Debout la France" = "right-wing populist",
  # left-wing populist
  "La France Insoumise" = "left-wing populist",
  "Compromís" = "left-wing populist",
  "En Comú Podem" = "left-wing populist",
  "Linke" = "left-wing populist",
  "Podemos" = "left-wing populist",
  # populist
  "Forza Italia" = "populist",
  "Gilets Jaunes" = "populist",
  "Movimento 5 Stelle" = "populist",
  "Potere al Popolo (PaP)" = "populist",
  # left-wing
  "EH Bildu" = "left-wing",
  "En Marea" = "left-wing",
  "ERC" = "left-wing",
  # "Foro Asturias" = "left-wing",
  "IU" = "left-wing",
  "Liberi e Uguali (LEU)" = "left-wing",
  # centre-left
  "Europe Écologie Les Verts" = "centre-left",
  "Grüne" = "centre-left",
  "Mouvement radical" = "centre-left",
  "Parti socialiste" = "centre-left",
  # centre-right
  "EAJ-PNV" = "centre-right",
  "Ciudadanos" = "centre-right",
  # "Agir, la droite constructive" = "centre-right",
  # right
  "La Destra" = "right",
  # centre
  "Mouvement démocrate" = "centre",
  "PDeCAT" = "centre",
  "Union des démocrates et indépendants" = "centre"))


conjoint$eupartyIDw2_type <- revalue(conjoint$eupostvotepartyW2, c(
  # mainstream
  "Génération.s, le mouvement" = "mainstream",
  "SPD" = "mainstream",
  "FDP" = "mainstream",
  "Partito Democratico (PD)" = "mainstream",
  "PSOE" = "mainstream",
  # mainstream right
  "La République En Marche!" = "mainstream right",
  "Les Républicains" = "mainstream right",
  "CDU/CSU" = "mainstream right",
  "+Europa / Radicali" = "mainstream right",
  "PP" = "mainstream right",
  # "Unione di Centro / Noi con l'Italia" = "mainstream right",
  # right-wing populist parties (or far-right?)
  "AfD" = "right-wing populist", 
  "Rassemblement national" = "right-wing populist",
  "Lega" = "right-wing populist",
  "Fratelli d'Italia" ="right-wing populist", 
  "VOX" = "right-wing populist",
  "Debout la France" = "right-wing populist",
  # left-wing populist
  "La France Insoumise" = "left-wing populist",
  "Compromís" = "left-wing populist",
  "En Comú Podem" = "left-wing populist",
  "Linke" = "left-wing populist",
  "Podemos" = "left-wing populist",
  # populist
  "Forza Italia" = "populist",
  "Gilets Jaunes" = "populist",
  "Movimento 5 Stelle" = "populist",
  "Potere al Popolo (PaP)" = "populist",
  # left-wing
  "EH Bildu" = "left-wing",
  "ERC" = "left-wing",
  "IU" = "left-wing",
  "Liberi e Uguali (LEU)" = "left-wing",
  # centre-left
  "Europe Écologie Les Verts" = "centre-left",
  "Grüne" = "centre-left",
  "Place Publique" = "centre-left",
  "Parti socialiste" = "centre-left",
  # centre-right
  "EAJ-PNV" = "centre-right",
  "Ciudadanos" = "centre-right",
  "Agir, la droite constructive" = "centre-right",
  # right
  "La Destra" = "right",
  # centre
  "PDeCAT" = "centre",
  "Union des démocrates et indépendants" = "centre"))


conjoint$partyIDcjnt_type <- revalue(conjoint$partyidclose_cjnt, c(
  # mainstream
  "Génération.s, le mouvement" = "mainstream",
  "SPD" = "mainstream",
  "FDP" = "mainstream",
  "Partito Democratico (PD)" = "mainstream",
  "PSOE" = "mainstream",
  # mainstream right
  "La République En Marche!" = "mainstream right",
  "Les Républicains" = "mainstream right",
  "CDU/CSU" = "mainstream right",
  "+Europa / Radicali" = "mainstream right",
  "PP" = "mainstream right",
  "Unione di Centro / Noi con l'Italia" = "mainstream right",
  # right-wing populist parties (or far-right?)
  "AfD" = "right-wing populist", 
  "Rassemblement national" = "right-wing populist",
  "Lega" = "right-wing populist",
  "Fratelli d'Italia" ="right-wing populist", 
  "VOX" = "right-wing populist",
  "Debout la France" = "right-wing populist",
  # left-wing populist
  "La France Insoumise" = "left-wing populist",
  "Compromís" = "left-wing populist",
  "En Comú Podem" = "left-wing populist",
  "Linke" = "left-wing populist",
  "Podemos" = "left-wing populist",
  # populist
  "Forza Italia" = "populist",
  "Movimento 5 Stelle" = "populist",
  "Potere al Popolo" = "populist",
  # left-wing
  "EH Bildu" = "left-wing",
  "En Marea" = "left-wing",
  "ERC" = "left-wing",
  "IU" = "left-wing",
  "Liberi e Uguali" = "left-wing",
  # centre-left
  "Europe Écologie Les Verts" = "centre-left",
  "Grüne" = "centre-left",
  "Mouvement radical" = "centre-left",
  "Parti socialiste" = "centre-left",
  "Place Publique" = "centre-left",
  # centre-right
  "EAJ-PNV" = "centre-right",
  "Ciudadanos" = "centre-right",
  "Agir, la droite constructive" = "centre-right",
  # right
  "La Destra" = "right",
  # centre
  "Mouvement démocrate" = "centre",
  "PDeCAT" = "centre"
  ))

```

```{r testing hypotheses with: prr vs lrr different samples, }

rw_populist <- conjoint %>% 
  rowwise() %>% 
  filter(any(c(partyID_type, partyvoteW2_type, eupartyIDw1_type, eupartyIDw2_type,
               partyIDcjnt_type) %in% c("right-wing populist"))) %>% 
  select(country, panelist_id, imm, soc, climate, eu, run, selected, partyID_type,
         partyvoteW2_type, eupartyIDw1_type, eupartyIDw2_type, partyIDcjnt_type)

lw_populist <- conjoint %>% 
  rowwise() %>% 
  filter(any(c(partyID_type, partyvoteW2_type, eupartyIDw1_type, eupartyIDw2_type,
               partyIDcjnt_type) %in% c("left-wing populist"))) %>% 
  select(country, panelist_id, imm, soc, climate, eu, run, selected, partyID_type,
         partyvoteW2_type, eupartyIDw1_type, eupartyIDw2_type, partyIDcjnt_type)


lw_populist <- anti_join(lw_populist, rw_populist)


rwp_result <- cregg::cj(
    rw_populist, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm")

lwp_result <- cregg::cj(
    lw_populist, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm")


rwp_result <- data.frame(rwp_result)
rwp_result$Voters <- rep("right-wing populist")
lwp_result <- data.frame(lwp_result)
lwp_result$Voters <- rep("left-wing populist")
combined_rlwp <- rbind(rwp_result, lwp_result)

ggplot(combined_rlwp, aes(estimate, level, colour=Voters)) +
  geom_point() + 
  geom_errorbarh(data = combined_rlwp, mapping=aes(y=level, xmax=lower, xmin=upper), 
                 height=0, size=0.5) + 
  geom_text(aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)), size = 1.5, 
            position = position_nudge(y = 0.4)) +
  scale_x_continuous(limits=c(0.25, 0.75)) +
  facet_wrap(~feature, scales="free_y", ncol=1) +
  geom_vline(xintercept = 0.5, linetype="solid", color = "black", size=0.2) +
  annotate("rect", xmin = 0.4, xmax = 0.6, ymin = -Inf, ymax = Inf, 
           fill = "black", alpha = 0.1, color = NA) +
  ggtitle("") +
  theme_bw() + 
  ylab("") + 
  xlab("Pr(Choosing a candidate)") +
  theme(axis.text=element_text(size=8), axis.title=element_text(size=8),
        title=element_text(size=10)) +
  scale_color_manual(values = c("#999999", "#000000"))

```

```{r rw populist and left-wing populist vs. all others, }


lr_populist <- conjoint %>% rowwise() %>% 
  filter(any(c(partyID_type, partyvoteW2_type, eupartyIDw1_type, eupartyIDw2_type,
               partyIDcjnt_type) %in% c("right-wing populist", "left-wing populist"))) %>% 
  select(country, panelist_id, imm, soc, climate, eu, run, selected, partyID_type,
         partyvoteW2_type, eupartyIDw1_type, eupartyIDw2_type, partyIDcjnt_type)

others <- anti_join(conjoint, lr_populist)

rl_result <- cregg::cj(
    lr_populist, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm")

others_result <- cregg::cj(
    others, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm")

rl_result <- data.frame(rl_result)
rl_result$Voters <- rep("left- and right-wing populist")
others_result <- data.frame(others_result)
others_result$Voters <- rep("others")
combined_rlo <- rbind(rl_result, others_result)

ggplot(combined_rlo, aes(estimate, level, colour=Voters)) +
  geom_point() + 
  geom_errorbarh(data = combined_rlo, mapping=aes(y=level, xmax=lower, xmin=upper), 
                 height=0, size=0.5) + 
  geom_text(aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)), size = 1.5, 
            position = position_nudge(y = 0.4)) +
  scale_x_continuous(limits=c(0.25, 0.75)) +
  facet_wrap(~feature, scales="free_y", ncol=1) +
  geom_vline(xintercept = 0.5, linetype="solid", color = "black", size=0.2) +
  annotate("rect", xmin = 0.4, xmax = 0.6, ymin = -Inf, ymax = Inf, 
           fill = "black", alpha = 0.1, color = NA) +
  ggtitle("") +
  theme_bw() + 
  ylab("") + 
  xlab("Pr(Choosing a candidate)") +
  theme(axis.text=element_text(size=8), axis.title=element_text(size=8),
        title=element_text(size=10)) +
  scale_color_manual(values = c("#999999", "#000000"))


```

```{r radical right wing populist vs. mainstream right, }

rmainstream <- conjoint %>% rowwise() %>% 
  filter(any(c(partyID_type, partyvoteW2_type, eupartyIDw1_type, eupartyIDw2_type,
               partyIDcjnt_type) %in% c("mainstream right"))) %>% 
  select(country, panelist_id, imm, soc, climate, eu, run, selected, partyID_type,
         partyvoteW2_type, eupartyIDw1_type, eupartyIDw2_type, partyIDcjnt_type)

rmainstream <- anti_join(rmainstream, rw_populist)

rmainstream_result <- cregg::cj(
    test, 
    selected ~ imm + soc + climate + eu + run,
    id = ~ panelist_id,
    estimate = "mm")

rmainstream_result <- data.frame(rmainstream_result)
rmainstream_result$Voters <- rep("mainstream right")
combined_mr <- rbind(rmainstream_result, rwp_result)

ggplot(combined_mr, aes(estimate, level, colour=Voters)) +
  geom_point() + 
  geom_errorbarh(data = combined_mr, mapping=aes(y=level, xmax=lower, xmin=upper), 
                 height=0, size=0.5) + 
  geom_text(aes(label = sprintf("%0.2f (%0.2f)", estimate, std.error)), size = 1.5, 
            position = position_nudge(y = 0.4)) +
  scale_x_continuous(limits=c(0.25, 0.75)) +
  facet_wrap(~feature, scales="free_y", ncol=1) +
  geom_vline(xintercept = 0.5, linetype="solid", color = "black", size=0.2) +
  annotate("rect", xmin = 0.4, xmax = 0.6, ymin = -Inf, ymax = Inf, 
           fill = "black", alpha = 0.1, color = NA) +
  ggtitle("") +
  theme_bw() + 
  ylab("") + 
  xlab("Pr(Choosing a candidate)") +
  theme(axis.text=element_text(size=8), axis.title=element_text(size=8),
        title=element_text(size=10)) +
  scale_color_manual(values = c("#999999", "#000000"))


```


